\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{datetime}
\usepackage{hyperref}

% https://tex.stackexchange.com/a/212264/273585
\newdateformat{monthyeardate}{\monthname[\THEMONTH] of \THEYEAR}

\begin{document}

\thispagestyle{empty}  % prevent page number on first page
                        % https://latex.org/forum/viewtopic.php?t=25462

Francisco Figari - Buenos Aires based computer scientist

\textit{Resume} - \monthyeardate\today

\url{http://ffig.ar/i}

\begin{itemize}

  \item Experience
  \begin{itemize}
    \item
      Ssr backend engineer @ \textit{Brubank} since May 2023. \newline
	  Extension and building of backend systems oriented to communicate
	  internal services, external services and backend-for-frontend
	  services. \newline
	  Extensive communication with mobile teams in order to build
	  reliable interfaces. \newline
	  Development of backoffice frontend which allowed customer service
	  to resolve tasks more easily. \newline
	  Introduction to monitoring and development in large scale systems.

    \item
      Research intern @ \textit{DC, FCEyN, UBA} between August 2021 and
      September 2022 under scholarship program for initiation in research.
      \newline
      Study about browser based eye tracking applied to remote clinical
      studies, work done around \textit{licenciatura} thesis.

    \item
      Fullstack programmer @ \textit{DubbingDigital} between March 2021 y
      December 2021.  \newline
      Development of web interface and web api of management software.

    \item
      Lead programmer @ \textit{UrbanSim} between July 2018 y November 2020.
      \newline
      Started with development of procedural generator of affordable housing,
      then switched to development of its evolving web platform.

    \item
      Research intern @ \textit{ARSLab, Carleton University} between February
      and June of 2018. \newline
      Study about applicability of simulation to the development of embedded
      systems' firmware.

    \item
      Teaching assistant in the Numerical Methods course @ \textit{DC, FCEyN,
      UBA}.  \newline
      4 semesters between 2016 y 2018 distributed between laboratory classes
      and theory classes.

    \item
      Freelance programmer @ \textit{LIAA, FCEyN, UBA} at the end of 2017.
      \newline
      Exploration of the use of eye tracking to the study of attention in
      static websites.

    \item
      Junior programmer @ \textit{Eryx} during 4 months at the beginning of
      2016.

    \item
      Kitchen helper and waiter @ \textit{La Capelina, San Fernando} during
      summers of 2012 and 2013.

  \end{itemize}

  \item Work skills
  \begin{itemize}

    \item
      Professional experience with multiple languages (\texttt{Golang},
      \texttt{JavaScript}, \texttt{C}\verb|++|, \texttt{Python}) and paradigms
      (objects, event driven, procedural). \newline
      Looking to learn new styles and applications of programming.

    \item
      Adoption of \textit{agile} practices and \textit{kanban} methodologies.
      Use of Jira. \newline
      Experience working in interdisciplinary teams consisting of
      \textit{backend}, \textit{mobile} and \textit{frontend} developers,
      managers, \textit{qa}, data scientists, urban planners and researchers.

	\item
	  Experience dealing with providers and leading small development teams
	  (between 2 and 3 developers).

    \item
      Ability to build web interfaces and web apis (\texttt{Bootstrap},
      \texttt{ExpressJS}, \texttt{Flask}). \newline
      Intermediate comprehension of \texttt{JavaScript}'s API to interact with
      the web browser. \newline
      Experience with reactive frontend libraries and frameworks
      (\texttt{ReactJS}, \texttt{VueJS}, \texttt{Redux}). \newline
      Basic knowledge about setting up, maintaining and migrating relational
      databases (\texttt{PostgreSQL}).

    \item
      Experience interpreting and working with urban planning zoning codes and
      geographic coordinate systems. \newline
      Manipulation of geospatial objects: drawing in frontend (\texttt{MapBox},
      \texttt{TurfJS}); storage (\texttt{PostGIS}); usage in algorithms.
      \newline
      Usage of geocodification APIs (\texttt{GoogleMaps Geocoding API}).

    \item
      Interest in applying and studying programming and development best
      practices. \newline
      Experience with Test Driven Development. \newline
      General knowledge about \texttt{Unix} systems (\texttt{git},
      \texttt{ssh}, \texttt{bash}). \newline
      Basic knowledge about \textit{DevOps} (\texttt{webpack},
      \texttt{kubernetes}, \texttt{gcp}).

    \item
      Native Spanish \newline
      Advanced English (daily usage for study and leisure) \newline
      Advanced French (schooling)

  \end{itemize}

  \item Studies
  \begin{itemize}
    \item
      Yoga teaching training program @ \textit{Red Prisma} between July 2023 and
      April 2025. \newline
      Introduction to asanas, meditation and breathing work. \newline
      Introduction to Buddhism. \newline
      Training to lead yoga classes.

    \item
      \textit{Licenciatura} in Computer Science @ \textit{DC, FCEyN, UBA},
      equivalent to Bachelor + Master with thesis,
      started in 2013 and finished in 2022.

    \item
      High school @ \textit{Licée Jean Mermoz, Buenos Aires}, finished in 2013.

  \end{itemize}

\end{itemize}

\end{document}

